A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-12-18 motivating_letter/motivating_letter.Rmd
clean for submission

---
from: Stephanie Kobakian
fromqualifications: MSc
fromemail: srkobakian@outlook.com
fromsignature: sigfile.png
toname: Michael Kane
toaddress: R Journal Editor
opening: Dear Mike,
closing: Best wishes
spacing: 1.4
output: MonashEBSTemplates::letter
---

>>>>

---
from: Stephanie Kobakian
fromqualifications: MPhil
fromtitle: Research Assistant
fromemail: srkobakian@outlook.com
fromsignature: sigfile.png
toname: Michael Kane
toaddress: R Journal Editor
opening: Dear Michael,
closing: Warm regards
spacing: 1.4
output: MonashEBSTemplates::letter
---
